Rstudio in Data Science and Paper Writing

### 2024-11-04 presentation/RStudio_paper_writing_course_presentation.qmd
Del part2: fused to part 1, add test slide transition

---
title: "Rstudio in Data Science and Paper Writing"
author: "Gáspár Jékely <br> Centre for Organismal Studies, Heidelberg University"
format:
  revealjs: 
    theme: [default, custom.scss]
    slide-number: false
    code-fold: false
    code-summary: "Code"
    chalkboard: 
      buttons: false
    preview-links: auto
scrollable: true
---

@@

## Most scientists use software developed for accounting

>>>>

---
title: "Rstudio in Data Science and Paper Writing"
author: "Gáspár Jékely <br> Centre for Organismal Studies, Heidelberg University"
format:
  revealjs: 
    theme: [default, custom.scss]
    slide-number: true
    code-fold: false
    code-summary: "Code"
    chalkboard: 
      buttons: false
    preview-links: auto
scrollable: true
---

@@

## Most scientists use software developed for accounting {transition="fade" transition-speed="fast"}
